\bf Model Visualization Techniques for a Social Network Model

### 2017-09-13 paper.Rnw
push uncommitted changes

<<senateplot, fig.cap='The collaboration network in the four senates during the Obama years, 2009-2016. Edges are shown only if the weighted propensity to cosponsor from one senator to another is greater than 0.25. We use the Fruchterman-Reingold algorithm to layout the node-link diagram.', fig.height=3>>=
seobama <- read_csv("data/congress/senateobamapres_gsw_25.csv")
to_label <- c("Joseph R. Biden Jr.", "John S. McCain", "Ted Cruz","Marco Rubio",
  "Lindsey O. Graham","Rand Paul", "Bernard Sanders", "Jim Webb", "Mitch McConnell",
  "Harry M. Reid", "Hillary Rodham Clinton")
seobama$label <- as.factor(ifelse(seobama$source %in% to_label, seobama$source, ""))
levels(seobama$label) <- c("", "Bernie Sanders", "Harry Reid", "Hillary Clinton", 
                           "Jim Webb", "John McCain", "Joe Biden", "Lindsey Graham",
                           "Marco Rubio", "Mitch McConnel", "Rand Paul", "Ted Cruz")
set.seed(56049382)
ggplot(data = seobama) + 
  geom_net(directed = T, labelon=T, arrowsize = .25, singletons= T, fiteach = T, linewidth = .25, layout.alg = 'fruchtermanreingold', fontsize = 2, repel=T,
           aes(from_id = source, to_id = target, color = party, label = label),
           size = 1) + 
  ThemeNet + 
  scale_color_manual(values = c("royalblue", "forestgreen","firebrick")) + 
  theme(legend.position = 'bottom') + 
  facet_wrap(~senate, nrow = 2, labeller = "label_both") + 
  xlim(c(0,1.05)) + 
  ylim(c(0,1.05))

>>>>

<<senateplot, fig.cap='The collaboration network in the four senates during the Obama years, 2009-2016. Edges are shown only if the weighted propensity to cosponsor from one senator to another is greater than 0.25. We use the Fruchterman-Reingold algorithm to layout the node-link diagram.', fig.height=3>>=
seobama <- read_csv("data/congress/senateobamapres_gsw_25.csv")
to_label <- c("Joseph R. Biden Jr.", "John S. McCain", "Ted Cruz","Marco Rubio",
  "Lindsey O. Graham","Rand Paul", "Bernard Sanders", "Jim Webb", "Mitch McConnell",
  "Harry M. Reid", "Hillary Rodham Clinton", "Amy Jean Klobuchar")
seobama$label <- as.factor(ifelse(seobama$source %in% to_label, seobama$source, ""))
levels(seobama$label) <- c("", "Amy Klobuchar", "Bernie Sanders", "Harry Reid",
                           "Hillary Clinton", "Jim Webb", "John McCain", "Joe Biden",
                           "Lindsey Graham", "Marco Rubio", "Mitch McConnel", 
                           "Rand Paul", "Ted Cruz")
set.seed(56049382)
ggplot(data = seobama) + 
  geom_net(directed = T, labelon=T, arrowsize = .25, singletons= T, fiteach = T, linewidth = .25, layout.alg = 'fruchtermanreingold', fontsize = 2, repel=T,
           aes(from_id = source, to_id = target, color = party, label = label),
           size = 1) + 
  ThemeNet + 
  scale_color_manual(values = c("royalblue", "forestgreen","firebrick")) + 
  theme(legend.position = 'bottom') + 
  facet_wrap(~senate, nrow = 2, labeller = "label_both") + 
  xlim(c(0,1.05)) + 
  ylim(c(0,1.05))
